\plaintitle

### 2017-04-26 statistical-quorum.tex
Adding a TODO.
Small improvements to introduction.

Traditionally it is argued that legitimacy comes from the fact that members had a chance to participate
and they decided not to, giving legitimacy to make a decision to those who did participate.
We argue that this is a problematic view because there are many restrictions on why members could not
participate and vote.
For example, they might not had time to participate because of other commitments, or motivation, or they might determined
that they are not informed enough to participate.
Moreover, members are from different reasons in their communities and potentially contribute in other ways
than by participating in its democratic processes.
Instead of assuming that everyone could participate if they would want, or trying to increase participation,
we can see amount of participation members are able to do as a limited resource, a \emph{collective attention}
a community has available to utilize.

We can compute decision credibility during ongoing voting process to give feedback to the community
on how contentious a proposed decision is how much more votes are necessary for a statistical quorum
to be reached.
This allows the community to focus its collective attention towards decisions which require more votes
to determine a legitimate result.
Instead of trying to increase participation on all democratic decisions being made, a community can
do that selectively through an automatic feedback loop.

To evaluate the use of statistical quorum in decision making of democratic communities we have developed
a web application PeerMind which integrates online discussion with online voting.
The application exposes computed decision credibility to users in real-time and through that provides
the feedback loop needed for improving utilization of collective attention.
We present the app in Section~\ref{sec:peermind}.

\todo[inline]{Structure of the rest of the paper.}

@@

@@

@@

>>>>

Traditionally it is argued that legitimacy comes from the fact that members had a chance to participate
and they decided not to, giving legitimacy to make a decision to those who did participate.
We argue that this is a problematic view because there are many restrictions on why members could not
participate and vote.
For example, they might not had time to participate because of other commitments, or motivation, or they might determined
that they are not informed enough to participate.
Moreover, members are from different reasons in their communities and potentially contribute in other ways
than by participating in its democratic processes.
Instead of assuming that everyone could participate if they would want, or trying to increase participation,
we can see amount of participation members are able to do as a limited resource, a \emph{collective attention}
a community has available to utilize for its decision making.

We can compute decision credibility during ongoing voting process to give feedback to the community
on how contentious a proposed decision is how much more votes are necessary for a statistical quorum
to be reached.
This allows the community to focus its collective attention towards decisions which require more votes
to determine a legitimate result.
Instead of trying to increase participation on all democratic decisions being made, a community can
do that selectively through an automatic feedback loop, trying to reach statistical quorum for their decisions.

We built an open source web application PeerMind integrating statistical quorum with online voting.
The application exposes computed decision credibility to users in real-time and through that provides
the feedback loop needed for improving utilization of collective attention.
We present the app in Section~\ref{sec:peermind} and use it for evaluating statistical quorum in
Section~\ref{sec:evaluation}.

\todo[inline]{Should we explicitly list our contributions again?}

\todo[inline]{Repeat the structure of the rest of the paper?}

@@

% repeat references from "There have been many improvements proposed to this basic form and various analysis made."?

% voting auditing

% delegation as way to increase legitimacy

@@

% theoretical: math, diagrams

% imperial: running it for x weeks in student community which has traditionally weekly meeting
% issues with quorum
% participation of everyone
% they used online app for x weeks
% we compare their old minutes with performance of new system

% interviews and surveys

@@

\section{Future Work}
